Appendix

### 2019-09-26 manuscript/appendix/appendix.Rmd
model estimate over all parameters

```{r message = FALSE}
library(tidyverse)
library(patchwork)
library(ggthemes)
library(furrr)
set.seed(12345)
```

@@

```{r}
r <- p$r
Q <- p$Q
K <- p$K
# a <- 2.3
H <- p$H
sigma <- p$sigma

r <- uniform(0, 2 * p$r)
Q <- uniform(0, 10)
K <- uniform(0, 2*p$K)
a <- uniform(0, 10)
H <- uniform(0,  2*p$H)
sigma <- uniform(0, 2 * p$sigma)

# Model   (mean <-  may(x_t, p))
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)
m <- model(a)
```

```{r }
system.time({
  draws <- mcmc(m, n_samples = 1000, warmup = 3000, chains = 4, verbose = FALSE)
})
```

@@

```{r}
#Q = 5
true <- 
  data.frame(a = 2.3) %>%
  gather(variable, value)
```

@@

posterior_samples %>%
  mutate(N=1e3, x0 = x0) %>%
  purrr::transpose() %>% map_dfr()

p$N <- 1e3

p$x0 <- x[[1]]
posterior_sims <- map_dfr(a, function(a){
  p$a <- a
  sim(may, p)
},
.id = "reps")

@@

true_forecast <- 
  future_map_dfr(1:100, 
                 function(reps) sim(may, p), 
                 .id = "reps"
                 ) %>% 
  mutate(t = t+2000) %>% 
  bind_rows(training_data) %>% 
  mutate(set = "true")

>>>>

```{r message = FALSE}
library(tidyverse)
library(patchwork)
library(ggthemes)
library(furrr)

library(greta)
tensorflow::use_session_with_seed(12345)

@@

```{r}

# a <- 2.3
r <- p$r
Q <- p$Q
K <- p$K
H <- p$H
sigma <- p$sigma

a <- uniform(0, 10)
r <- uniform(0, 2 * p$r)
#Q <- uniform(0, 10)
K <- uniform(0, 2*p$K)
H <- uniform(0,  2*p$H)
sigma <- uniform(0, 2 * p$sigma)

# Model   (mean <-  may(x_t, p))
mean <- x_t + r * x_t * (1 - x_t / K) - a * x_t ^ Q / (x_t ^ Q + H ^ Q)
distribution(x_t1) <- normal(mean, sigma * x_t)

m <- model(a, r, K, H, sigma)
```

```{r }

system.time({
  draws <- mcmc(m, n_samples = 1000, warmup = 3000, chains = 4, verbose = FALSE)
})
```

@@

```{r}
#Q = 5
true <- 
  as_tibble(p) %>% select(-N, -x0, -Q) %>%
  gather(variable, value)
```

@@

posterior_sims <- posterior_samples %>%
  mutate(N=1e3, x0 = x0, Q = p$Q) %>% 
         ## sigma = p$sigma, H = p$H, K = p$K, r = p$r) %>%
  purrr::transpose() %>%
  map_dfr(function(q) sim(may, q) ,.id = "reps")
```

```{r}
#q <- posterior_samples[1,] %>%  mutate(N=1e3, x0 = x0, Q = p$Q)
#sim(may, q)

#posterior_sims <- map_dfr(a, function(a){
#  p$a <- a
#  sim(may, p)
#},
#.id = "reps")

@@

p$x0 <- x0
p$N <- 1e3
true_forecast <- 
  future_map_dfr(1:100, 
                 function(reps) sim(may, p), 
                 .id = "reps"
                 ) %>% 
  mutate(t = t+2000) %>% 
  bind_rows(training_data) %>% 
  mutate(set = "true")
